A Review on Interactive Adaptive Processes Which Underline Short-Term Motor Learning

### 2022-06-25 Report/PaperReport.tex
abstract is added

\begin{abstract}
Abstract
\end{abstract}

>>>>

\begin{abstract}

Multiple models have tried to simulate the motor skill acquisition but most of them fail in producing some of the features of motor skill learning. Here a model is demonstrated that within a timescale of minutes, two distinct fast-acting processes drive motor adaptation. One process responds weakly to error but retains information well, whereas the other responds strongly but has poor retention. This two-state learning system is capable of prediction of spontaneous recovery (adaptation rebound) if error feedback is zeros. Our results suggest that motor adaptation depends on at least two distinct neural systems that have different sensitivity to error and retain information at different rates. Also, the motor skill learning will be more if the changes in the environment are slow.
\end{abstract}
